Unknown

### 2024-04-09 ms/ms.qmd
drafting tbl-predictions

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS?
- TABLE SUMMARIZING PARAMETERS

>>>>

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS?
- TABLE SUMMARIZING PARAMETERS
model | fixed effects | phylogenetic random effects | response to native PPFD
1 | light intensity | varying intercept among accessions | AA_0,acc
1 | light treatment | | 
2 | light intensity | varying intercept among accessions | AA_0,acc
2 | light treatment | | 
2 | light intensity x light treatment | | 
3 | light intensity | varying intercept among accessions | AA_2000,acc
3 | light treatment | varying effect of high light intensity among accessions | 
4 | light intensity | varying intercept among accessions | AA_sun,acc
4 | light treatment | varying effect of sun treatment among accessions | 
5 | light intensity | varying intercept among accessions | AA_2000,high,acc
5 | light treatment | varying effect of high light intensity among accessions | 
5 | light intensity x light treatment | varying effect of sun treatment among accessions |

### 2024-04-09 ms/test.qmd
drafting tbl-predictions

Manual curation of a data set this size in a principled, consistent manner is not feasible. Therefore, we automated data cleaning using custom *R* scripts. Cleaning is divided into six sequential steps \autoref{tbl-parameters}.

```{r, parameters, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-parameters
#| tbl-cap: "caption"

df_parameters = read_csv("../data/parameters1.csv", col_types = "cccc", n_max = 6)

df_parameters |>
  dplyr::select(Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("c", "l"),
    booktabs = TRUE,
    escape = FALSE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) #|>
                        # kableExtra::pack_rows("x", 2, 2)

>>>>

blah \autoref{tbl-predictions}.

```{r, predictions, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-predictions
#| tbl-cap: "caption"

df_parameters |>
  tribble(
    Parameter = latex, Description = description) |>
  knitr::kable(
    format = "latex",
    align = c("l", "l"),
    booktabs = TRUE,
    escape = FALSE,
    longtable = TRUE
  ) |>
  kableExtra::kable_styling(latex_options = c("striped", "no_vertical_lines")) |>
  kableExtra::column_spec(1, width = "1in") |>
  kableExtra::column_spec(2, width = "5in") |>
  kableExtra::pack_rows("\\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "ags")),
                        max(which(df_parameters$par_type == "ags")),
                        escape = FALSE) |>
  kableExtra::pack_rows("\\aax{} for each light intensity with leaf using \\agcurve{} curve parameters",
                        min(which(df_parameters$par_type == "aa_est")),
                        max(which(df_parameters$par_type == "aa_est")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects light intensity, light treatments, and accession on \\aax",
                        min(which(df_parameters$par_type == "aa")),
                        max(which(df_parameters$par_type == "aa")),
                        escape = FALSE) |>
  kableExtra::pack_rows("effects of native light habitat on accession-level \\aax",
                        min(which(df_parameters$par_type == "ppfd_aa")),
                        max(which(df_parameters$par_type == "ppfd_aa")),
                        escape = FALSE)
